Inference for Trans-dimensional Bayesian Models with Diffusive Nested Sampling

### 2014-12-07 Documents/Paper/ms.tex
footnote

\subsection{Diffusive Nested Sampling}
The main difficulty with Nested Sampling is coming up with methods to sample
the constrained prior distributions of Equation~\ref{eq:constrained_prior}.
Various implementations of Nested Sampling exist, with different strategies
for sampling Equation~\ref{eq:constrained_prior}
\citep[e.g.][]{multinest, diamonds, radfriends}.

Diffusive Nested Sampling
\citep[DNS][]{dnest} is an alternative version of Nested Sampling that is
appropriate when MCMC is used to explore the parameter space.
A C++ implementation of DNS, called {\tt DNest3}, is available at
{https://github.com/eggplantbren/DNest3}.

>>>>

\subsection{Diffusive Nested Sampling}
The main difficulty with Nested Sampling is coming up with methods to sample
the constrained prior distributions of Equation~\ref{eq:constrained_prior}.
Various implementations of Nested Sampling exist, with different strategies
for sampling Equation~\ref{eq:constrained_prior}
\citep[e.g.][]{multinest, diamonds, radfriends}.
Diffusive Nested Sampling
\citep[DNS][]{dnest} is an alternative version of Nested Sampling that is
appropriate when MCMC is used to explore the parameter space\footnote{
A C++ implementation of DNS, called {\tt DNest3}, is available at
{\tt https://github.com/eggplantbren/DNest3}}.
